---
title: "ShinyAppPresentation"
author: "M.Farkov"
date: '2017-03-14'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Simple Shiny application

This is very simple application but it demonstrates basic concept of Shiny-like application quite well. The main goal of application is calculation of factorial for numbers in interval [1,10].

## Interface
```{r echo=FALSE}
library(png)
png<-readPNG('app1.png')
plot(1:300,ty='n',axes = FALSE,ann=FALSE)
rasterImage(png,1,1,300,250)
```

## ui.R
ui.R code includes sidebar panel and main panel, In main panel you can find input slider. Calculated factorial values are printed in main pain.
```{r echo=TRUE,eval=FALSE}
library(shiny)
shinyUI(fluidPage(
  titlePanel("Calculate factorial"),
  sidebarLayout(
    sidebarPanel(
        h3('Please select value for factorial calculation'),
       sliderInput("input","factorial of",min = 1,max = 10,value = 10)
    ),
    mainPanel(h3('Factorial value'),textOutput('result'))
    )))
```


## server.R
server.R code is very simple. It takes input value which is stored in variable `input`, calculates factorial and places result to outpu variable `result`.
```{r echo=TRUE,eval=FALSE}
library(shiny)
shinyServer(function(input, output) {
  output$result <- renderText(factorial(input$input))
})
```